Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-05 manuscript.Rmd
Null models - v1

df_personality <- # create final df for analyses
df_personality %>% 
  pivot_longer(cols = judgment_trait1:informant_trait26,
               names_to = c("trait", "item"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(item = parse_number(item)) %>% # could not write the correct regex :(
  pivot_wider(names_from = "trait",
              values_from = "rating") %>% 
  right_join(., trait_norms, by = "item") %>% 
  mutate(self_dist = target - self_norm,
         inf_dist = informant - inf_norm
         )

@@

## Thought
df_thought <- import(here::here("data", "d_thought.csv")) %>% 
  select(PerUn, TarUn, DyUn, Group, BaselineEA:CrrctdEAnoneg) %>% 
  rename_at(vars(PerUn:Group), ~ 
              c("perceiver_id", "target_id", "dyad_id", "group_id")
             ) %>% 
  left_join(., select(df_personality, perceiver_id:group_id,
                      InsecAtt:Trust, rapport_c))

@@

```{r null models}
null_trait_self <- lmer(judgment ~ 
                (1|perceiver_id) + 
                (1|target_id) + 
                (1|dyad_id) +
                (1|group_id),
              data = df_personality)
```

```{r}
# affect
samEACaggdata <- import(here::here("data", "c_affect.csv"))

samEAC_null <- lmer (Part ~ 1 + 
                  (1|PerUn) + 
                  (1|TarUn) + 
                  (1|DyUn) +
                    (1|Group), 
                data = samEACaggdata)

sjPlot::tab_model(samEAC_null, null_affect)

summary(samEAC_null)

null_affect <- lmer(judgment ~ 1 + 
                  (1|perceiver_id) + 
                  (1|target_id) + 
                  (1|dyad_id) +
                    (1|group_id), 
                data = df_affect)

@@

```{r}
# thought

# overall EA
SRMdat1 <- lmer(EA100 ~ 
                   (1|PerUn) + 
                   (1|TarUn) + 
                   (1|DyUn) + 
                   (1|Group), 
                 data = eaSRMdata)

sjPlot::tab_model(SRMdat1)
```

>>>>

df_personality <- # create final df for analyses
df_personality %>% 
  pivot_longer(cols = judgment_trait1:informant_trait26,
               names_to = c("trait", "item"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(item = parse_number(item)) %>% # could not write the correct regex :(
  pivot_wider(names_from = "trait",
              values_from = "rating") %>% 
  right_join(., trait_norms, by = "item") %>% 
  mutate(self_dist = target - self_norm,
         inf_dist = informant - inf_norm,
         across(self_norm:inf_dist, center)
         )

@@

## Thought
df_thought <- import(here::here("data", "d_thought.csv")) %>% 
  select(PerUn, TarUn, DyUn, Group, BaselineEA:CrrctdEAnoneg) %>% 
  rename_at(vars(PerUn:Group), ~ 
              c("perceiver_id", "target_id", "dyad_id", "group_id")
             ) %>% 
  left_join(., select(df, perceiver_id:group_id,
                      InsecAtt_c:rapport_c)) %>% 
  rename(judgment = EA100)

@@

```{r null models}
df_list <- list(df_personality,
                df_affect,
                df_thought)

null_models <- df_list %>% 
  map_dfr(
    ~ lmer(judgment ~ (1|perceiver_id) + 
             (1|target_id) + 
             (1|dyad_id),
           data = .x) %>% 
      broom.mixed::tidy()
    )

null_models %>% 
  kable_style(title = "<center><b>Null Models</b></center>") %>% 
  kableExtra::pack_rows("Personality", 1, 5) %>% 
  kableExtra::pack_rows("Affect", 6, 10) %>% 
  kableExtra::pack_rows("Thought", 11, 15)

by_model <- 
null_models %>% 
  mutate(model = c(rep("p", 5), rep("a", 5), rep("t", 5))
         ) %>% 
  group_by(model) %>% 
  nest()

map(by_model, specr::plot_variance)

fill_color <- "#377eb8"

null_models2 <- df_list %>% 
  map(
    ~ lmer(judgment ~ (1|perceiver_id) + 
             (1|target_id) + 
             (1|dyad_id),
           data = .x)
    )

map(null_models2, performance::icc, by_group = TRUE)

@@
